Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-29 main.tex
Completed the algorithm text for the whole protocol Added missing labels to all encoding and our scheme equations (used these in the protocol instead of giving equations) Added missing index i for sensor locations (obviously these are dependent on the sensor Added missing index 0 to public key of our scheme (this is how the notation is when we define it) Fixed EIF update equations which were using the wrong index (k-1 just used in the prediction step) - this should still be done in a nicer way, currently x_k updated from x_k which is not really true in an equation Fixed error when defining pri

\begin{description}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose an $m>1$ as the number of weights to combine, and set public parameter $\mathsf{pub}=H$, aggregator public key $pk_0 = N$ and aggregator private key $sk_0=(p,q)$. The remaining user secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}$.

    \item[$\mathsf{Enc}(pk_0, \omega)$] Encryption of weights is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
    \begin{equation}
        \mathcal{E}_{pk_0}(\omega) = (N+1)^{\omega}r^N \pmod{N^2}\,,
    \end{equation}
    for a randomly chosen $r \in \mathbb{Z}_N$.

@@

    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
    \begin{equation}
        \begin{split}
            \sum^{n}_{i=1}\sum^{m}_{j=1}&x^{(t)}_{i,j}\omega^{(t)}_j =\\
            &\frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,.
        \end{split}
    \end{equation}
    The correctness of aggregation can be seen from
    \begin{align*}
        y^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r_i^N \pmod{N^2} \\
        \begin{split}
            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N \pmod{N^2}
        \end{split}\\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}\,,
    \end{align*}
    for some values $r_i,r' \in \mathbb{Z}_N,\,1\leq i \leq n$.
\end{description}

@@

The combined quantisation and encoding function $\mathsf{E}_{r,f,m}(x)$ of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_N$, and the desired scaling for $m$ prior encoded multiplications, is given by
\begin{equation}
    \mathsf{E}_{N,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{N}\,. \label{eqn:encode}
\end{equation}
Decoding of an integer $e \in \mathbb{Z}_N$, is given by
\begin{equation}
    \mathsf{E}^{-1}_{N,f,m}(e) \!=\! 
    \begin{dcases}
        \frac{e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &e\hspace{-8pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
        -\frac{N - e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &\text{otherwise} \\
    \end{dcases}.
\end{equation}

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
\begin{equation}
    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \rvec{y}_k = \rvec{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobian
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
\begin{equation}
    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
\end{equation}
and
\begin{equation}
    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k-1}}\,. \label{eqn:jacobian_f}
\end{equation}

@@

\subsection{Localisation Measurement Model} \label{subsec:observation_model}
Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator. In addition, the Jacobian of $h_i$,
\begin{equation}
    \mat{H}_{k,i} = 
    \begin{bmatrix}
        \frac{\rv{x}_k - s_x}{\sqrt{(\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2}} \\
        \frac{\rv{y}_k - s_y}{\sqrt{(\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2}} 
    \end{bmatrix}\,,
\end{equation}
cannot be either. Instead, we consider the modified measurement functions
\begin{equation}
    h'_i(\rvec{x}_k) = h_i(\rvec{x}_k)^2\,. \label{eqn:modified_measurement_func}
\end{equation}
A measurement function in this form allows rearrangement to a linear combination of navigator information, and thus of the corresponding modified measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ as well. The modified measurement functions $h'_i$ can be written as
\begin{equation}
    \begin{split}
        h'_i(\rvec{x}_k) &= \left\lVert
        \begin{bmatrix}
            \rv{x}_k & \rv{y}_k
        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
        &= (\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2 \\
        &= \rv{x}_k^2 + \rv{y}_k^2 -2s_x\rv{x}_k -2s_y\rv{y}_k +s_x^2 +s_y^2
    \end{split}\,,
\end{equation}
and the corresponding Jacobians $\mat{H}'_{k,i}$ as
\begin{equation}
    \mat{H}'_{k,i} = 
    \begin{bmatrix}
        2\rv{x}_k - 2s_x \\
        2\rv{y}_k - 2s_y
    \end{bmatrix}\,.
\end{equation}
The above have been rearranged as linear combinations of the weights $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which capture all the required information that is private to the navigator.

@@

With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
\begin{equation}
    \begin{split}
        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
        &= 
        \begin{bmatrix}
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_x)\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{x}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_x^3) + (2\rv{r}_{k,i}^{-1}s_xs_y^2) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x \rv{z}'_{k,i})
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y)\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{y}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_ys_x^2) + (2\rv{r}_{k,i}^{-1}s_y^3) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y\rv{z}'_{k,i})
            \end{split}
        \end{bmatrix}
    \end{split} \label{eqn:hrz_linear_comb}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
        &=
        \begin{bmatrix}
            \alpha_{11} & \alpha_{12} \\
            \alpha_{21} & \alpha_{22}
        \end{bmatrix}\,,
    \end{split} \label{eqn:hrh_linear_comb}
\end{equation}
with
\begin{align*}
    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_x)\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_x^2) \\
    \begin{split}
        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_y)\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_x)\rv{y}_k \\
        &\qquad+ (4\rv{r}_{k,i}^{-1}s_xs_y)
    \end{split}\\
    \alpha_{21} &= \alpha_{12} \\
    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_y)\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_y^2)\,.
\end{align*}
The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.

@@

\begin{algorithm}
    \caption{Navigator Prediction Step}\label{alg:nav_prediction}
    \begin{algorithmic}[1]
        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$}
        \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
        \State $\rvec{x}_{k} \gets \vec{f}(\rvec{x}_{k-1})$
        \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$
        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
            \State $r \gets$ \Call{RandInt}{$1,N$}
            \State $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega})) \gets (N+1)^{\mathsf{E}_{0}(\rv{\omega})}r^N \pmod{N^2}$
            \State Broadcast $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
        \EndFor
        \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

>>>>

\begin{description}
    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$. Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose an $m>1$ as the number of weights to combine, and set public parameter $\mathsf{pub}=H$, aggregator public key $pk_0 = N$ and aggregator private key $sk_0=(p,q)$. The remaining user secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.

    \item[$\mathsf{Enc}(pk_0, \omega)$] Encryption of weights is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
    \begin{equation}
        \mathcal{E}_{pk_0}(\omega) = (N+1)^{\omega}r^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
    \end{equation}
    for a randomly chosen $r \in \mathbb{Z}_N$.

@@

    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
    \begin{equation}
        \begin{split}
            \sum^{n}_{i=1}\sum^{m}_{j=1}&x^{(t)}_{i,j}\omega^{(t)}_j =\\
            &\frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,.
        \end{split} \label{eqn:our_scheme_decrypt}
    \end{equation}
    The correctness of aggregation can be seen from
    \begin{align*}
        y^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r_i^N \pmod{N^2} \\
        \begin{split}
            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N \pmod{N^2}
        \end{split}\\
        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}\,,
    \end{align*}
    for some values $r_i,r' \in \mathbb{Z}_N,\,1\leq i \leq n$.
\end{description}

@@

The combined quantisation and encoding function $\mathsf{E}_{r,f,m}(x)$ of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_N$, and the desired scaling for $m$ prior encoded multiplications, is given by
\begin{equation}
    \mathsf{E}_{N,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{N}\,. \label{eqn:encode}
\end{equation}
Decoding of an integer $e \in \mathbb{Z}_N$, is given by
\begin{equation}
    \mathsf{E}^{-1}_{N,f,m}(e) \!=\! 
    \begin{dcases}
        \frac{e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &e\hspace{-8pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
        -\frac{N - e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &\text{otherwise} \\
    \end{dcases}.\label{eqn:decode}
\end{equation}

@@

\subsection{Extended Information Filter}
The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor. This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
\begin{equation}
    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
\end{equation}
respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
\begin{equation}
    \rvec{y}_k = \rvec{y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
\end{equation}
and
\begin{equation}
    \mat{Y}_k = \mat{Y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
\end{equation}
with Jacobian
\begin{equation}
    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
\end{equation}
for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
\begin{equation}
    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
\end{equation}
before using the normal EKF prediction equations
\begin{equation}
    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
\end{equation}
and
\begin{equation}
    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
\end{equation}
with Jacobian
\begin{equation}
    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k-1}}\,. \label{eqn:jacobian_f}
\end{equation}

@@

\subsection{Localisation Measurement Model} \label{subsec:observation_model}
Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator. In addition, the Jacobian of $h_i$,
\begin{equation}
    \mat{H}_{k,i} = 
    \begin{bmatrix}
        \frac{\rv{x}_k - s_{x,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} \\
        \frac{\rv{y}_k - s_{y,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} 
    \end{bmatrix}\,,
\end{equation}
cannot be either. Instead, we consider the modified measurement functions
\begin{equation}
    h'_i(\rvec{x}_k) = h_i(\rvec{x}_k)^2\,. \label{eqn:modified_measurement_func}
\end{equation}
A measurement function in this form allows rearrangement to a linear combination of navigator information, and thus of the corresponding modified measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ as well. The modified measurement functions $h'_i$ can be written as
\begin{equation}
    \begin{split}
        h'_i(\rvec{x}_k) &= \left\lVert
        \begin{bmatrix}
            \rv{x}_k & \rv{y}_k
        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
        &= (\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2 \\
        &= \rv{x}_k^2 + \rv{y}_k^2 -2s_{x,i}\rv{x}_k -2s_{y,i}\rv{y}_k +s_{x,i}^2 +s_{y,i}^2
    \end{split}\,,
\end{equation}
and the corresponding Jacobians $\mat{H}'_{k,i}$ as
\begin{equation}
    \mat{H}'_{k,i} = 
    \begin{bmatrix}
        2\rv{x}_k - 2s_{x,i} \\
        2\rv{y}_k - 2s_{y,i}
    \end{bmatrix}\,.
\end{equation}
The above have been rearranged as linear combinations of the weights $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which capture all the required information that is private to the navigator.

@@

With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
\begin{equation}
    \begin{split}
        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
        &= 
        \begin{bmatrix}
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{x}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_{x,i}^3) + (2\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i}^2) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i} \rv{z}'_{k,i})
            \end{split}
            \vspace{5pt}\\
            \begin{split}
                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k^2 \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{y}_k \\
                &\quad+ (2\rv{r}_{k,i}^{-1}s_{y,i}s_{x,i}^2) + (2\rv{r}_{k,i}^{-1}s_{y,i}^3) \\
                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}\rv{z}'_{k,i})
            \end{split}
        \end{bmatrix}
    \end{split} \label{eqn:hrz_linear_comb}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
        &=
        \begin{bmatrix}
            \alpha_{11} & \alpha_{12} \\
            \alpha_{21} & \alpha_{22}
        \end{bmatrix}\,,
    \end{split} \label{eqn:hrh_linear_comb}
\end{equation}
with
\begin{align*}
    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
    \begin{split}
        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k \\
        &\qquad+ (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})
    \end{split}\\
    \alpha_{21} &= \alpha_{12} \\
    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
\end{align*}
The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.

@@

\begin{algorithm}
    \caption{Navigator Prediction Step}\label{alg:nav_prediction}
    \begin{algorithmic}[1]
        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$}

        \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
        \State $\rvec{x}_{k} \gets \vec{f}(\rvec{x}_{k-1})$
        \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$

        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
            \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ by \eqref{eqn:our_scheme_encrypt}
            \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
        \EndFor

        \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
    \caption{Measurement at Sensor $i$}\label{alg:measurement_info}
    \begin{algorithmic}[1]
        \Procedure{Measurement}{$i$, $s_{x,i}$, $s_{y,i}$, $r_i$, $N$, $H$}

        \State Measure $\rv{z}_{k,i}$
        \State Compute $\rv{z}_{k,i}'$ by \eqref{eqn:modified_measurement}
        \State Compute $\rv{r}_{k, i}$ by \eqref{eqn:modified_meaasurement_variance_estimate}

        \While{Navigator broadcasting}
        \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))$
        \State Recieve remaining weights in the form above
        \EndWhile

        \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
        \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}$\par
        \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k\rv{y}^2_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}
        \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_{x,i})}$\par
        \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{y}^2_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i})}
        \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}$\par
        \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i}^2)}
        \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{y,i}^2)}$\par
        \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}^3)}
        (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}s_{y,i}^2)}$\par
        \ $(N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_{x,i}\rv{z}_{k,i}')}
        H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
        \State Compute $\beta_{21}^{(i)}$ using \eqref{eqn:hrz_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
        \For{$v \gets 1$ to $2$}
            \State Send $\beta_{v1}$ to the navigator
        \EndFor

        \State Let $\alpha_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
        \State $\alpha_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}$\par
        \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}
        (N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_{x,i}^2)}$\par
        \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
        \State Compute remaining $\alpha_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
        \For{$v \gets 1$ to $2$}
            \For{$w \gets 1$ to $2$} 
                \State Send $\alpha_{vw}^{(i)}$ to the navigator
            \EndFor
        \EndFor
        \EndProcedure
    \end{algorithmic}
\end{algorithm}
